DataGatheringandAnalysis

### 2014-11-13 GEMDataSource.Rmd
Added scatterplotmatrix
Adding control variable

# Install rempis from Christpher Gandrud's website

# Library Repmis, Tidy, Reshape2, and plyr packages
library(repmis)
library(tidyr)
library(reshape2)
library(plyr)

@@

### Clean FearFail ###

@@

### Clean CurrentOwner ###
# Remove X's in CurrentOwner year columns
names(CurrentOwner) <- gsub("X", "", names(CurrentOwner))

@@

### Clean EntreIntention ###
# Remove X's in EntreIntention year columns
names(EntreIntention) <- gsub("X", "", names(EntreIntention))

@@

### Clean PerceivedCapabilities ###
# Remove X's in PerceivedCapabilities year columns
names(PerceivedCapabilities) <- gsub("X", "", names(PerceivedCapabilities))

@@

# Plot graph
car::scatterplotMatrix(FinalMerge)
```

>>>>

# Library Repmis, Tidy, Reshape2, and plyr packages
library(repmis)
library(tidyr)
library(reshape2)
library(plyr)
library(WDI)

@@

### Clean FearFail ###
# Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from seeting up a business.

@@

### Clean CurrentOwner ###
# Percentage of 18-64 population who are currently owner-manager of an established business, i.e., owning and managing a running business that has paid sallaries, wages, or any other payments to the owners for more than 42 months

# Remove X's in CurrentOwner year columns
names(CurrentOwner) <- gsub("X", "", names(CurrentOwner))

@@

### Clean EntreIntention ###
# Percentage of 18-64 population (individuals involved in any stage of entrepenerurial activity excluded) who intend to start a business within three years.

# Remove X's in EntreIntention year columns
names(EntreIntention) <- gsub("X", "", names(EntreIntention))

@@

### Clean PerceivedCapabilities ###
# Percentage of 18-64 population who believe to have the required skills and knowledge to start a business

# Remove X's in PerceivedCapabilities year columns
names(PerceivedCapabilities) <- gsub("X", "", names(PerceivedCapabilities))

@@

# Plot graph
car::scatterplotMatrix(FinalMerge)

#### Import WDI Annual GDP Growth Data ####
WDIsearch('gdp')
dat = WDI(indicator='GDP growth (annual %)', country=c('MX','CA','US',), start=2001, end=2013)

```
